---
title: "Detect CS/WOS anomalies"
---

Upload the data and packages.
```{r}
library (dplyr)
library (ggplot2)
library (ggpubr)

df = read.csv('C:/Users/jchang/Desktop/Projects/Funnel Anomaly Detection/data/CSWOSAnomalyDetectionTrainingDatav3_2018-12-19_1432.csv')
head(df)
```


The data is normal, therefore we can calculate simple Confidence Interval.
```{r}
hist(df$cs_wos,
     breaks = 2^7
     # , xlim = c(0.4,1.2)
)
ggdensity(df$cs_wos)
ggqqplot(df$cs_wos)

shapiro.test(df$cs_wos)
```



Confidence Intervals.
```{r}

mu = mean(df$cs_wos)
sd = mean(df$cs_wos)*(1-mean(df$cs_wos))

c(mu-1.96*sd, mu+1.96*sd)

```





The data is skewed, therefore we will use calculate significance based on Bootstrap-t Confidence Intervals.
```{r}
hist(df$cs_wos,
     breaks = 2^7
     # , xlim = c(0.4,1.2)
)
ggdensity(df$cs_wos)
ggqqplot(df$cs_wos)

shapiro.test(df$cs_wos)

# hist(df$cs_wos[which(df$wosdate >= as.Date('2018-10-01') &
#                      df$wosdate <= as.Date('2018-10-31') &
#                      df$hour >= 6 &
#                      df$hour <= 18 &
#                      df$dow >= 1 &
#                      df$dow <= 5)],
#      breaks = 2^7)


```


Write the bootstrap function to make future life easier.
```{r}

bootstrap_t_ci = function (x, B, n_b, alpha_decimal){
  
  # Create storage vectors
  theta_b = vector(length = B)
  sigma_b = vector(length = B)
  z_b = vector(length = B)
  
  # Calculate the mean of the underlying distribution.
  theta = mean(df$cs_wos)
  
  # Create B Re-samples
  for (i in 1:B){
    resample_b = sample(
      x = df$cs_wos,
      size = n_b,
      replace = TRUE
    )
  
  # For each resample, calculate:
    ## Its mean.
    theta_b[i] = mean(resample_b)
    
    ## Its standard error.
    sigma_b[i] = sd(resample_b)/sqrt(n_b)
    
    ## Its Z, and record this in a sorted vector.
    z_b[i] = (theta_b[i]-theta)/sigma_b[i]
  
  }
  
  # Calculate the standard error of the underlying distribution.
  se = sd(theta_b)
  
  # Calculate the confidence interval.
  lower = (1-alpha_decimal)/2
  upper = (1-alpha_decimal)/2 + alpha_decimal
  
  ci = theta - se*quantile(z_b, c(upper, lower)) # Yes, these are supposed to be switched
  names(ci) = c(lower, upper)
  
  return(ci)
}




bootstrap_percentile_ci = function (x, B, n_b, alpha_decimal){
  
  # Create storage vectors
  theta_b = vector(length = B)
  
  # Create B Re-samples
  for (i in 1:B){
    resample_b = sample(
      x = df$cs_wos,
      size = n_b,
      replace = TRUE
    )
  
  # For each resample, calculate:
    ## Its mean.
    theta_b[i] = mean(resample_b)
  }
  
  # Calculate the confidence interval.
  ci = quantile(theta_b, c(lower, upper))
  
  return(ci)
}

```


How does the bootstrap do on CS/WOS?
```{r}

# Training on ALL DATA
print('All')
bootstrap_t_ci(x = df$cs_wos,
               B = 1000,
               n_b = 10,
               alpha_decimal = 0.95)

bootstrap_percentile_ci(x = df$cs_wos,
                        B = 1000,
                        n_b = 10,
                        alpha_decimal = 0.95)


# Training on 11/1/2018 - 11/14/2018 MONDAYS
# print('All, Normal')
# bootstrap_t_ci(x = df$cs_wos[which(df$wosdate >= as.Date('2018-10-01') &
#                                    df$wosdate <= as.Date('2018-10-31') &
#                                    df$hour >= 6 &
#                                    df$hour <= 18 &
#                                    df$dow >= 1 &
#                                    df$dow <= 5)],
#                B = 1000,
#                n_b = 10,
#                alpha_decimal = 0.95)

```

Which apps fall out of the confidence interval?

```{r}

length(df$cs_wos[which(df$cs_wos < 0.8293449)])
length(df$cs_wos[which(df$cs_wos < 0.8293449)])/length(df$cs_wos)

```




ggplot for periscope.

```{r}
library(ggplot2)

df = read.csv('C:/Users/jchang/Desktop/Projects/Funnel Anomaly Detection/data/CSWOSMonitoring_2018-12-19_1623.csv')

qplot(round(df$cs_wos,2), 
      geom = 'histogram',
      binwidth = 0.005)

ggplot(data = df, aes(x = cs_wos, color = grouping, fill = grouping)) +
  geom_density(alpha = 0.2)

# ggplot(data = df, aes(x = cs_wos)) +
#   geom_bar(aes(y = ))

head(df)

```